\documentclass{beamer}

% Define the title, author, and date for the title slide
\title{My First Beamer Presentation}
\author{John Doe}
\date{\today}

% Start the document environment
\begin{document}

% Create the title slide
\begin{frame}
    \titlepage
\end{frame}


\begin{frame}{Overview}
   \begin{itemize}
   \item Introduction: Skills, experience and motivation
   \item Review business problems and solutions
   \begin{itemize}
   		\item Classifying text messages
   		\item Forecasting time series
   		\item  Recommendations
   		\item Generating letters
   		\item Summarizing content
   		\end{itemize}
   	\item Conclusion and next steps
   \end{itemize}
\end{frame}


\section{Introduction}
% First content slide
\begin{frame}{Introduction}

Computer Scientist, data scientist and sometimes finance quant

Coded in mny languages (Fortrn, C++, Java, Matlab, SAS)
  but now almost exclusively Python and the Python ecosystem
  
    \begin{itemize}
        \item This is a basic Beamer presentation.
        \item Slides are created using the \texttt{frame} environment.
        \item You can use standard LaTeX commands inside each frame.
    \end{itemize}
\end{frame}
% --- The main content of your presentation ---
\section{Classifying text mesages}
% First content slide
\begin{frame}{Introduction}
    \begin{itemize}
        \item This is a basic Beamer presentation.
        \item Slides are created using the \texttt{frame} environment.
        \item You can use standard LaTeX commands inside each frame.
    \end{itemize}
\end{frame}

\section{Regression}
% Second content slide
\begin{frame}{Key Features}
    \begin{itemize}
        \item Easy typesetting of mathematical equations.
        \item High-quality and consistent layout.
        \item Simple creation of lists and tables.
    \end{itemize}
\end{frame}

% Slide with an equation
\begin{frame}{Example Equation}
    This is an example of an equation in a Beamer slide.
    $$E=mc^2$$
\end{frame}

% End the document environment
\end{document}
